Growth model analysis 3spp WB

### 2019-03-15 MS_Analysis_3spp_4rivers_Patterns_from 2spp.Rmd
add pairwise by variables for gam

vB$speciesRiver <- factor(paste(vB$speciesOrdered,vB$riverOrdered, sep = '_'), ordered = T)

@@

@@

mod6sr <- bam(observedLength ~ cohort * species * river + 
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', by = speciesRiver), 
             data = vB %>% filter(cohort %in% 2000:2013,species %in% c('bkt','bnt')), method = "REML")
summary(mod6sr)

predGrid <- expand.grid(speciesRiver = unique(mod6sr$model$speciesRiver),
                        cohort = 2000:2013,
                        ydayCumul = seq(250,1000, by = 30)) %>%
                 mutate(species = substr(speciesRiver,1,3),
                        river = substring(speciesRiver,5))

pred <- predict(mod6sr, newdata = predGrid)#, type = 'lpmatrix')

>>>>

vB$speciesRiver <- factor(paste(vB$speciesOrdered,vB$riverOrdered, sep = '_'), ordered = T)
vB$speciesCohort <- factor(paste(vB$speciesOrdered,vB$cohortOrdered, sep = '_'), ordered = T)
vB$cohortRiver <- factor(paste(vB$cohortOrdered,vB$riverOrdered, sep = '_'), ordered = T)

@@

# by cohortSpeciesRiver - model is overfit

@@

# by speciesRiver

mod6SR <- bam(observedLength ~ cohort * species * river + 
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', by = speciesRiver), 
             data = vB %>% filter(cohort %in% 2000:2013,species %in% c('bkt','bnt')), method = "REML")
summary(mod6sr)

predGridSR <- expand.grid(speciesRiver = unique(mod6SR$model$speciesRiver),
                        cohort = 2000:2013,
                        ydayCumul = seq(250,1000, by = 30)) %>%
                 mutate(species = substr(speciesRiver,1,3),
                        river = substring(speciesRiver,5))

predSR <- predict(mod6SR, newdata = predGrid)#, type = 'lpmatrix')

predGrid2SR <- bind_cols(predGridSR,as.data.frame(predSR))

ggplot(predGrid2SR, aes(ydayCumul,pred, color = species)) +
  geom_point() + 
  geom_line() +
  facet_grid(river ~ cohort)

# by speciesCohort

mod6SC <- bam(observedLength ~ cohort * species * river + 
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', by = speciesCohort), 
             data = vB %>% filter(cohort %in% 2000:2013,species %in% c('bkt','bnt')), method = "REML")
summary(mod6SC)

predGridSC <- expand.grid(speciesCohort = unique(mod6SC$model$speciesCohort),
                        river = unique(vB$riverOrdered),
                        ydayCumul = seq(250,1000, by = 30)) %>%
                 mutate(species = substr(speciesCohort,1,3),
                        cohort = as.numeric(substring(speciesCohort,5)))

predSC <- predict(mod6SC, newdata = predGridSC)#, type = 'lpmatrix')

predGrid2SC <- bind_cols(predGridSC,as.data.frame(predSC))

ggplot(predGrid2SC, aes(ydayCumul,predSC, color = species)) +
  geom_point() + 
  geom_line() +
  facet_grid(river ~ cohort)

# by cohortRiver

mod6CR <- bam(observedLength ~ cohort * species * river + 
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', by = cohortRiver), 
             data = vB %>% filter(cohort %in% 2000:2013,species %in% c('bkt','bnt')), method = "REML")
summary(mod6CR)

predGridCR <- expand.grid(cohortRiver = unique(mod6CR$model$cohortRiver),
                        species = c('bkt','bnt'),
                        ydayCumul = seq(250,1000, by = 30)) %>%
                 mutate(cohort = as.numeric(substr(cohortRiver,1,4)),
                        river = (substring(cohortRiver,6)))

predCR <- predict(mod6CR, newdata = predGridCR)#, type = 'lpmatrix')

predGrid2CR <- bind_cols(predGridCR,as.data.frame(predCR))

ggplot(predGrid2CR, aes(ydayCumul, predCR, color = species)) +
  geom_point() + 
  geom_line() +
  ylim(50,200) +
  facet_grid(river ~ cohort)
